%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Arttu}{Modig}{
% \urlstyle{same}\href{http://debarghyadas.com}{debarghyadas.com}| \href{http://fb.co/dd}{fb.co/dd}\\
\href{mailto:arttu.modig@gmail.com}{arttu.modig@gmail.com} | +358 45 320 5550 (WhatsApp, Telegram, Signal)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Aalto University}
\descript{M.Sc. (Tech.) in Bioinformation Technology}
\location{Oct 2016 | Espoo, Finland}
\location{Major: {\it Computational and Cognitive Biosciences}}
%\location{Thesis: {\it A Metric for Human Motor\\Capacity}}
\vspace{0.2em}
\descript{B.Sc. (Tech.) in Bioinformation Technology}
\location{Nov 2015 | Espoo, Finland}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://facebook.com/amodig}{\bf amodig} \\
Github:// \href{https://github.com/amodig}{\bf amodig} \\
LinkedIn:// \href{https://www.linkedin.com/in/amodig}{\bf amodig} \\
Twitter:// \href{https://twitter.com/ArttuModig}{\bf @ArttuModig} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Data Science}
\location{Expert \& loving:}
Product Analytics \textbullet{} BI \textbullet{} Data Analysis, Engineering \& Visualization \textbullet{} Bayesian Statistics \textbullet{} Machine Learning \\
\location{I've worked extensively with:}
A/B testing \textbullet{} Airflow \textbullet{} BigQuery \textbullet{} ETL \\
Looker \textbullet{} Superset \textbullet{} CRM \textbullet{} KPIs \\
\location{Other technologies I've used:}
RDBMS \textbullet{} NoSQL \textbullet{}
Big Data (Hadoop, Spark, Cloudera, HP Vertica) \textbullet{} AWS \\
Google Cloud (Analytics, Kubernetes, Tag~Manager)
\sectionsep
\subsection{Programming}
\location{Expert/Working knowledge:}
Python (OOP, pytest, Jupyter, pandas, SciPy, matplotlib) \textbullet{} SQL \textbullet{} Docker \textbullet{} Git\\
 R (tidyverse, ggplot2) \textbullet{} Jira \textbullet{} Matlab \\ Java \textbullet{} GNU/Linux \textbullet{}\LaTeX \\ 
\location{Experience:}
HTML5 \textbullet{} CSS \textbullet{} JavaScript \\
Shell scripting (Bash, ZSH) \textbullet{} Stan \\
C \textbullet{} PHP \textbullet{} Scala \textbullet{} Processing
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HOBBIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobbies}
BoardGameGeek:// \href{https://boardgamegeek.com/user/dalar}{\bf Dalar} \\
Goodreads:// \href{https://goodreads.com/amodig}{\bf amodig} \\
RateYourMusic:// \href{https://rateyourmusic.com/~Dalar}{\bf Dalar} \\
reading \textbullet{} music \textbullet{} films \textbullet{} nature \\
rock climbing \textbullet{} yoga \textbullet{} meditation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Business Experience}
\runsubsection{Wolt}
\descript{| Product Data Analyst}
\location{Oct 2020 – | Helsinki, Finland}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Member of the Performance Marketing team and later Marketing Tech team.
\end{tightemize}

\runsubsection{Armada Interactive}
\descript{| Data Scientist}
\location{Dec 2017 – Sep 2020 | Helsinki, Finland}
\begin{tightemize}
\item Data-informed product design and development with the use of in-game analytics.
\item Data engineering and automated dashboard analytics: ETL, data modeling (Airflow \& BigQuery) and data visualization (Superset) with Google Cloud (incl. customized Kubernetes environments).
\end{tightemize}

\runsubsection{Veikkaus}
\descript{| Data Scientist}
\location{Jan 2017 – Dec 2017 | Helsinki, Finland}
\begin{tightemize}
\item Member of the Operational Analytics team in Digital Marketing, Sales and CR.
\item Web analytics \& optimization (A/B testing orchestration), automated KPIs, performance attribution, CRM analysis \& visualization, and general (Explorative) Data Analysis and and Machine Learning.
\end{tightemize}
%\sectionsep

\runsubsection{RAY}
\descript{| Data Analyst \& Software Developer}
\location{Apr 2015 – Dec 2016 | Espoo, Finland}
\begin{tightemize}
\item Member of the Game Studio UX/UI team and later BI team.
\item BI data mining, predictive modelling, reporting automation, computational UX/UI personalization, in-game analytics, A/B testing, and general EDA and ML.
\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Experience}
\runsubsection{Helsinki Institute of Information Technology}
\descript{| Research Assistant}
\location{2011 – May 2015 | Helsinki, Finland}
\begin{tightemize}
\item Member of the Information, Complexity and Learning research group led by Assistant Prof. Teemu Roos (part of CoSCo).
\item Applied information theory, machine learning and Bayesian statistics.
\item Created software and services, e.g. a full LAMP production service and a recommendation engine backend service in Python.
\end{tightemize}
%\sectionsep

\runsubsection{Max Planck Institute for Informatics}
\descript{| Research Assistant}
\location{Jul 2012 – Sep 2012 | Saarbrücken, Germany}
\begin{tightemize}
\item Computational HCI research led by Ph.D. Antti Oulasvirta.
\end{tightemize}
%\sectionsep

\runsubsection{Department of Micro and Nanosciences, Aalto University}
\descript{| Research Assistant}
\location{2009 – 2011 | Espoo, Finland}
\begin{tightemize}
\item Member of the Photonics research group led by Prof. Seppo Honkanen. Extensive experience with laboratory setups and working in a clean room space with chemical handling.
\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\renewcommand\refname{\vskip -0.8cm} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications_arttu}
%\nocite{*}
Please see: \href{https://dblp.org/pers/hd/m/Modig:Arttu}{https://dblp.org/pers/hd/m/Modig:Arttu}

\end{minipage} 
\end{document} \documentclass[]{article}
